\bf Manifold Clustering in the Generalized Random Dot Product Graph

### 2022-06-20 draft/draft.Rmd
syncing stuff

One common analysis task for graph and network data is community detection, which assumes that each vertex of a graph has a hidden community label. The goal of the analysis is then to retrieve these labels. In order to perform this analysis as a statistical inference task is to define a probability model with inherent community structure. We call such models *block models*: 
First, each vertex is assigned a label $z_1, ..., z_n \in \{1, 2, ..., K\}$ where $K \ll n$. 
Then each edge probability $P_{ij}$ is said to depend on the labels $z_i$ and $z_j$, possibly along with some other parameters. 
For example, the stochastic block model (SBM) sets a fixed edge probability for each pair of communities, i.e., $P_{ij} = \omega_{z_i, z_j}$. 
The degree-corrected block model (DCBM) assigns an additional parameter $\theta_i$ to each vertex by which edge probabilities are scaled, i.e., $P_{ij} = \theta_i \theta_j \omega_{z_i, z_j}$. 
The popularity adjusted block model (PABM) assigns $K$ parameters to each vertex $\lambda_{i1}, \lambda_{i2}, ..., \lambda_{iK}$ that describe that vertex's affinity toward each community; 
the edge probability between vertices $i$ and $j$ is then defined as the product of vertex $i$'s affinity toward vertex $j$'s community and vertex $j$'s affinity toward vertex $i$'s community, i.e., $P_{ij} = \lambda_{i z_j} \lambda_{j z_i}$.

@@

\begin{enumerate}
  \item Draw labels $z_1, ..., z_n \iid \Multinomial(\alpha_1, ..., \alpha_K)$. 
  \item Draw latent vectors by first drawing each $t_i \indep F_{z_i}$ and then computing each $x_i = g_{z_i}(t_i)$. 
  \item Let $X = \begin{bmatrix} x_1 & \cdots & x_n \end{bmatrix}^\top$, and draw $A \sim \RDPG(X)$ or $A \sim \GRDPG_{p,q}(X)$. 
\end{enumerate}
\end{definition}

@@

Xhat <- embedding(A, 2, 0)
plot(Xhat, col = z, asp = 1)
```

>>>>

One common analysis task for graph and network data is community detection, which assumes that each vertex of a graph has a hidden community label. The goal of the analysis is then to estimate these labels upon observing a graph. 
In order to perform this analysis as a statistical inference task is to define a probability model with inherent community structure. We call such models *block models*: 
First, each vertex is assigned a label $z_1, ..., z_n \in \{1, 2, ..., K\}$ where $K \ll n$. 
Then each edge probability $P_{ij}$ is said to depend on the labels $z_i$ and $z_j$, possibly along with some other parameters. 
For example, the stochastic block model (SBM) sets a fixed edge probability for each pair of communities, i.e., $P_{ij} = \omega_{z_i, z_j}$. 
The degree-corrected block model (DCBM) assigns an additional parameter $\theta_i$ to each vertex by which edge probabilities are scaled, i.e., $P_{ij} = \theta_i \theta_j \omega_{z_i, z_j}$. 
The popularity adjusted block model (PABM) assigns $K$ parameters to each vertex $\lambda_{i1}, \lambda_{i2}, ..., \lambda_{iK}$ that describe that vertex's affinity toward each community; 
the edge probability between vertices $i$ and $j$ is then defined as the product of vertex $i$'s affinity toward vertex $j$'s community and vertex $j$'s affinity toward vertex $i$'s community, i.e., $P_{ij} = \lambda_{i z_j} \lambda_{j z_i}$.

@@

\begin{enumerate}
  \item Draw labels $z_1, ..., z_n \iid \Multinomial(\alpha_1, ..., \alpha_K)$. 
  \item Draw latent vectors by first drawing each $t_i \indep F_{z_i}$ and then compute each $x_i = g_{z_i}(t_i)$. 
  \item Let $X = \begin{bmatrix} x_1 & \cdots & x_n \end{bmatrix}^\top$, and draw $A \sim \RDPG(X)$ or $A \sim \GRDPG_{p,q}(X)$. 
\end{enumerate}
\end{definition}

@@

Xhat <- embedding(A, 2, 0)
n <- nrow(Xhat)
plot(Xhat, col = z, asp = 1)
```

### 2022-06-20 draft/draft.tex
syncing stuff

One common analysis task for graph and network data is community
detection, which assumes that each vertex of a graph has a hidden
community label. The goal of the analysis is then to retrieve these
labels. In order to perform this analysis as a statistical inference
task is to define a probability model with inherent community structure.
We call such models \emph{block models}: First, each vertex is assigned
a label \(z_1, ..., z_n \in \{1, 2, ..., K\}\) where \(K \ll n\). Then
each edge probability \(P_{ij}\) is said to depend on the labels \(z_i\)
and \(z_j\), possibly along with some other parameters. For example, the
stochastic block model (SBM) sets a fixed edge probability for each pair
of communities, i.e., \(P_{ij} = \omega_{z_i, z_j}\). The
degree-corrected block model (DCBM) assigns an additional parameter
\(\theta_i\) to each vertex by which edge probabilities are scaled,
i.e., \(P_{ij} = \theta_i \theta_j \omega_{z_i, z_j}\). The popularity
adjusted block model (PABM) assigns \(K\) parameters to each vertex
\(\lambda_{i1}, \lambda_{i2}, ..., \lambda_{iK}\) that describe that
vertex's affinity toward each community; the edge probability between
vertices \(i\) and \(j\) is then defined as the product of vertex
\(i\)'s affinity toward vertex \(j\)'s community and vertex \(j\)'s
affinity toward vertex \(i\)'s community, i.e.,
\(P_{ij} = \lambda_{i z_j} \lambda_{j z_i}\).

@@

\begin{enumerate}
  \item Draw labels $z_1, ..., z_n \stackrel{\mathrm{iid}}{\sim}\mathrm{Multinomial}(\alpha_1, ..., \alpha_K)$. 
  \item Draw latent vectors by first drawing each $t_i \stackrel{\mathrm{ind}}{\sim}F_{z_i}$ and then computing each $x_i = g_{z_i}(t_i)$. 
  \item Let $X = \begin{bmatrix} x_1 & \cdots & x_n \end{bmatrix}^\top$, and draw $A \sim \mathrm{RDPG}(X)$ or $A \sim \mathrm{GRDPG}_{p,q}(X)$. 
\end{enumerate}
\end{definition}

@@

@@

>>>>

One common analysis task for graph and network data is community
detection, which assumes that each vertex of a graph has a hidden
community label. The goal of the analysis is then to estimate these
labels upon observing a graph. In order to perform this analysis as a
statistical inference task is to define a probability model with
inherent community structure. We call such models \emph{block models}:
First, each vertex is assigned a label
\(z_1, ..., z_n \in \{1, 2, ..., K\}\) where \(K \ll n\). Then each edge
probability \(P_{ij}\) is said to depend on the labels \(z_i\) and
\(z_j\), possibly along with some other parameters. For example, the
stochastic block model (SBM) sets a fixed edge probability for each pair
of communities, i.e., \(P_{ij} = \omega_{z_i, z_j}\). The
degree-corrected block model (DCBM) assigns an additional parameter
\(\theta_i\) to each vertex by which edge probabilities are scaled,
i.e., \(P_{ij} = \theta_i \theta_j \omega_{z_i, z_j}\). The popularity
adjusted block model (PABM) assigns \(K\) parameters to each vertex
\(\lambda_{i1}, \lambda_{i2}, ..., \lambda_{iK}\) that describe that
vertex's affinity toward each community; the edge probability between
vertices \(i\) and \(j\) is then defined as the product of vertex
\(i\)'s affinity toward vertex \(j\)'s community and vertex \(j\)'s
affinity toward vertex \(i\)'s community, i.e.,
\(P_{ij} = \lambda_{i z_j} \lambda_{j z_i}\).

@@

\begin{enumerate}
  \item Draw labels $z_1, ..., z_n \stackrel{\mathrm{iid}}{\sim}\mathrm{Multinomial}(\alpha_1, ..., \alpha_K)$. 
  \item Draw latent vectors by first drawing each $t_i \stackrel{\mathrm{ind}}{\sim}F_{z_i}$ and then compute each $x_i = g_{z_i}(t_i)$. 
  \item Let $X = \begin{bmatrix} x_1 & \cdots & x_n \end{bmatrix}^\top$, and draw $A \sim \mathrm{RDPG}(X)$ or $A \sim \mathrm{GRDPG}_{p,q}(X)$. 
\end{enumerate}
\end{definition}

@@

rves clustering.\} \textbackslash end\{algorithm\}

@@

upervised \(K\)-curves clustering.\} \textbackslash end\{algorithm\}
